---
title: "Numerical Methods for Engineers"
author: "John Hamre III"
date: "August 10, 2017"
output: slidy_presentation
---


## Problem

- Using the volume of a sphere and r= 3mm we get Vi=113.04 uL.
The time is from 0 to 40 in 0.25 minute increments of 10 total minutes.
- For 10 minutes at -0.1mm/minute rate we should lose 1mm total from the radius to 2mm therefore Vf=33.4933 uL
- Solve for "r" with volume formula and sub that into "r" of the area formula gives the following code solution with graph.

## Solvong usind the ODE function in R

```{r, warning=FALSE, message=FALSE}

library(mosaic)
soln = integrateODE(dx~ (((-.1*(((x*3)/(4*3.14))^(1/3))^2*3.14*4)*.25)),x=113.04,tdur=list(from=0,to=100))
soln$x(40)  #0.25 for 10 is 40
plotFun(soln$x(t)~t,t.lim=range(0,120), ylab = "V (uL)", xlab = "t (15 s/unit)")

```

## Solving using the Euler method with loop

```{r, echo=FALSE}


i=0
x=113.04
while (i < 41) {	
  print(x)		
   x = { ((-.1*(((x*3)/(4*pi))^(1/3))^2*pi*4)*.25) + x}		
        		
   i= (i +1) }	


```





